% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
%
% This document has been modified heavily by Josiah Couch.
%

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

%Fix spacing after sections
\usepackage[compact]{titlesec}  
\titlespacing{\section}{0pt}{*0}{*0}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Josiah Couch}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {physics, mathematics},
  pdftitle = {\name: resume},
  pdfsubject = {resume},
  pdfpagemode = UseNone
}

\geometry{
  %body={6.5in, 8.5in},
  left=0.25in,
  right=0.25in,
  top=0.15in,
  bottom=0.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large\bf\sectionrule{0ex}{0pt}{-1ex}{1pt}}
\subsectionfont{\rmfamily\mdseries\bf\normalsize}
\subsubsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}
%Control spacing between lines and after paragraphs
\setlength{\parskip}{0em}
\renewcommand{\baselinestretch}{0}

% Section spacings
\usepackage{titlesec}
\titlespacing*{\section}{0em}{0em}{0em}
\titlespacing*{\subsection}{0em}{0em}{0em}
\titlespacing*{\subsubsection}{0em}{0em}{0em}


% Control lists
\renewenvironment{itemize}{
  \begin{list}{$\bullet$}{
    \setlength{\itemsep}{0em}
    \setlength{\parskip}{0em}
    \setlength{\parsep}{0em} 
    \setlength{\topsep}{0em} 
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
%{\huge \name}

% Alternatively, print name centered:
\centerline{\LARGE \name}

\begin{center}

\small{\textbf{Email}: josiah.couch@utexas.edu \textbf{Website}: \url{josiahcouch.com}}

\end{center}

\section*{Education}

\subsection*{University of Texas at Austin, Austin, TX}
\subsubsection*{Ph.D in Physics (3.6 GPA) \hfill August 2013 - May 2020 (expected)}

\begin{itemize}
\item Adviser: Willy Fischler
\item Dissertation Title: "Circuit Complexity in QFT and Holography" (tentative).

\item Courses: Quantum Mechanics 1, Classical Mechanics, Statistical Mechanics, Electromagnetic Theory 1, Quantum Field Theory 1 \& 2, Relativity Theory 1, String Theory 1 \& 2, Algebraic Topology, Representation Theory.
\end{itemize}

%\subsection*{Technische Universit\"at M\"unchen, Garching, Bavaria, Germany}
%\subsubsection*{Study Abroad \hfill October 2012 - August 2013}

%\begin{itemize}
%\item Courses: Functional Analysis, Introduction to Quantum Field Theory, German (A2), Spanish (B2/C1).
%\end{itemize}

\subsection*{Oklahoma State University, Stillwater, Oklahoma}
\subsubsection*{B.S in Physics and B.S. in Mathematics \hfill August 2009 - August 2013}

\begin{itemize}
\item 10 Months study abroad at the Technical University of Munich, Munich, Bavaria, Germany.
\end{itemize}

\section*{Experience}

\subsection*{University of Texas at Austin, Austin, TX} 
\subsubsection*{Ph.D. Candidate \hfill August 2013 - Present}
    \begin{itemize}
    
        \item Four papers published in peer-reviewed journals and an additional two under review with over 180 citations, four conference presentations, and numerous internal presentations.
        \item Regularly collaborate with other physicists to do original research, especially at the intersection of quantum information and quantum gravity.
 %       \item Formulate interesting and solvable problems, mainly related to the AdS/CFT correspondence and its intersection with quantum information theory.
%        \item Solve quantitative problems in a collaborative environment with software tools, especially Wolfram Mathematica.
%        \item Present findings to colleagues through presentations both internally at UT and externally at conferences. 
        
    \end{itemize}
    
\subsubsection*{Teaching Assistant \hfill August 2013 - Present}
    \begin{itemize}
    
        \item Provide supplemental instruction on course material and problem-solving techniques to students in review sessions.
        \item Create official solutions to problem sets and grade student submissions.
        %\item Responsible for lab sections, including instruction, evaluation, and student safety.
        \item Courses TAed include graduate and undergraduate quantum mechanics, the lab for engineering physics, and classical electrodynamics.
        
    \end{itemize}
    
\subsubsection*{Graduate Research Assistant with Center for Particles and Fields under Prof. Peter Onyisi \hfill June - July 2014}
    \begin{itemize}
    
    	\item Worked on data analysis and python programming at CERN's campus in Meyrin, Switzerland.
        \item Used pyROOT and TMVA machine learning package to study feature importance in a classification task.
        \item Wrote a script in python to retrieve information about the state of the ATLAS detector from a COOL database.
        
    \end{itemize}
    
\subsection*{Max Planck Institut f\"ur Physik, Munich, Bavaria, Germany}

\subsubsection*{Scientific Assistant with Experimental Particle Physics Group, six-week contract \hfill April- May 2013}
    \begin{itemize}
        \item Tested and calibrated pixel detectors for ATLAS upgrade. 
    \end{itemize}

\subsection*{Oklahoma State University, Stillwater, OK}
\subsubsection*{Undergraduate Researcher in Experimental Particle Physics Group under Prof. Flera Rizatdinova \hfill January 2010 - May 2012}
    \begin{itemize}
        \item Used C++ and ROOT package for event classification and, ultimately, for estimation of the number of signal events.
        \item Presented work in a poster and live presentations.
    \end{itemize}
    
%\subsubsection*{Computer Lab Monitor with DASNR Technology Services and %Support \hfill August 2009 - December 2011}
%    \begin{itemize}
%        \item Responsible for maintaining and (remotely) monitoring three %computer labs along with printers.
%        \item Assisted DASNR faculty members and staff with software %installation.
%        \item Replaced hard drives, power supplies, memory sticks, et cetera in %desktop computers.
%    \end{itemize}

\section*{Skills}

{\bf Soft Skills:} Quantitative Problem Solving, Research, Advanced Mathematics

{\bf Technologies:}
\begin{itemize}
	\item[] Intermediate: Python, Git, Mathematica, LaTex, 
	\item[] Beginner: SQL%, Linux, Java, C++, Javascript, Haskell
\end{itemize}
 

%{\bf Languages:} Spanish (intermediate), German (beginner)

\section*{Interests}

Quantum Gravity, Quantum Information Theory, Programming, Data Science, Photography, Video Games, Languages

\end{document}
